Measurement of the positive kaon-argon total hadronic differential cross section in the LArIAT experiment

### 2018-03-14 Drafting.tex
s

The Liquid Argon Time Projection Chamber (LArTPC) can be broken down into three major subcomponents: $1)$ The high voltage system which provides the drift field voltage; $2)$ the cathode and field cage which steps down the high voltage through a network of voltage-dividing resistors to form a uniform electric field for charges to drift within; and $3)$ the wire planes which provide the charge sensitive readout for the detector. Here we describe each of the subcomponents which make up the LArIAT LArTPC.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}{High Voltage}\label{sec:DriftVoltage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The drift high voltage system for the LArIAT detector, shown pictorially in Figure~\ref{fig:HVScheme}, is designed to allow ionization electrons from the interaction of charged particles in the liquid argon to drift to the wireplanes. The high voltage system consists of a Glassman LX125N16 power supply~\cite{GlassmanPS} capable of generating -125~kV and 16~mA of current. This power supply was typically operated much below this limit during normal data taking operations. The voltage from the power supply is transmitted through high voltage cables to a series of filter pots before finally reaching the high-voltage feedthrough on the top of the LArIAT cryostat. This feedthrough brings the voltage into the liquid argon volume to be transmitted to the TPC cathode.

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{./figures/HVSchematic.png}\\
\caption{Schematic of the LArIAT high voltage system.}
\label{fig:HVScheme}
\end{figure}%See DocDB 1472

The first high voltage cable which connects the Glassman power supply to the first filter pot is a 1/2-inch HV cable, Glassman cable model 2121, supplied by the Glassman manufacturer. The second cable is a $\sim$100-ft long 1/2-inch Type-2134 Dielectric Sciences cable which connects the first filter pot to the second filter pot. Finally, the same type of cable is used to connect the second filter pot to the high voltage feedthrough at the cryostat.

The two filter pots that are inline with the high voltage system serve to: $a)$ limit the current draw on the power supply; $b)$  provide a low-pass filter to help reduce the voltage ripple on the cathode; and $c)$ partition the energy stored in the system in the event of a high voltage trip. Each filter pot, as shown in Figure~\ref{fig:FilterPot}, is a cylindrical aluminum pot 18.5 inches tall by 20 inches in diameter and 3/16 inches thick, with welded tops each having an opening that allows for a flange and o-ring to receive the high voltage cables. Within each pot, the flanges are connected to four 10~M$\Omega$ resistors connected in series. This assembly is submerged in $\sim$16 gallons of Diala transformer oil~\cite{ShellDiala} to aid in the suppression of corona and discharges.

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{./figures/FilterPot.png}\\
\caption{Filter pots used in the LArIAT high voltage system.}
\label{fig:FilterPot}
\end{figure}%See DocDB 1472

The final piece of the high voltage system is the high voltage feedthrough which delivers the drift voltage to the cathode of the TPC. This feedthrough is based on a a custom design that was used by ICARUS \cite{IcarusDetector}. The feedthrough consists of a stainless steel inner conductor surrounded by a tube of ultra high molecular weight polyethylene further surrounded by a stainless steel outer ground tube. The high-voltage feedthrough enters the cryostat from a dedicated 4-5/8 inch Conflat flange at the top of the cryostat. The end of the inner conductor is finally attached to the cathode by a flexible conductor bolted at both ends. A technical drawing of the LArIAt high voltage feedthrough can be found in Figure \ref{fig:HVFT}.

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{./figures/lariatFeedthrough.pdf}\\
\caption{Technical drawing of the LArIAT high voltage feedthrough. Various liquid argon levels are shown in cyan to indicate the levels to ensure the feedthrough is immersed in argon during operations}
\label{fig:HVFT}
\end{figure}%See DocDB 1472

During usual operations, the operating voltage from the Glassman power supply was -23.5~kV corresponding to a drift field of $\sim$500 V/cm. During special runs, the high voltage system was operated in a range from 0~kV to 32.8~kV (corresponding to drift fields ranging from 0~V/cm to 700~V/cm) and the feedthrough was tested up to 60~kV with no electrical breakdown observed.

\end{subsubsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}{Cathode and Field Cage}\label{sec:FieldCage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textcolor{red}{Description of the cathode and field cage is missing}

As shown in Figure \ref{fig:driftregions}, the LArIAT TPC has three drift volumes, each of which has its own electric field. The main drift volume is defined as the region between the cathode plane and the shield plane (C-S). Note that the shield plane wires are \emph{not} read out. The other two drift regions are those between the shield plane and the induction plane (S-I), and between the induction plane and the collection plane (I-C). The electric field in these regions is chosen to satisfy the charge transparency condition to allow for 100$\%$ transmission of the drifting electrons through the shield and then the induction planes. We provide a detailed description of the electric field measurement in each region in \ref{sec:EFieldMeasurements}.

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{./images/DriftRegions.png}\\
\caption{Schematic of the three drift regions inside the LArIAT TPC: the main drift volume between the cathode and the shield plane (C-S) in green, the region between the shield plane and the induction plane (S-I) in purple, and the region between the induction plane and the collection plane (I-C) in pink.}
\label{fig:driftregions}
\end{figure}

Table \ref{tab:voltages} provides the default voltages applied to the cathode and the shield, induction, and collection plane for all the runs. These voltages were tuned to maintain the transparency condition when the (I-C) and (S-I) spacing changed. For data taken in Run-I, Run-II, and Run-IIIb the spacing was a constant 4~mm; the spacing was 5~mm for Run-IIIa.

\begin{table}[htpb]
\centering
\caption{Anode planes default voltages}
\label{tab:voltages}
\begin{tabular}{lllll}
\hline
\multicolumn{1}{|l|}{V Cathode} & 
\multicolumn{1}{|l|}{V Shield} & \multicolumn{1}{l|}{V Induction} & \multicolumn{1}{l|}{V Collection} & \multicolumn{1}{|l|}{Run} \\ \hline
\multicolumn{1}{|l|}{-23.17 kV} &
\multicolumn{1}{|l|}{-298.8 V} & \multicolumn{1}{l|}{-18.5 V}      & \multicolumn{1}{l|}{338.5 V} & \multicolumn{1}{|l|}{Run-I, Run-II \& Run-IIIb}      \\ \hline
\multicolumn{1}{|l|}{-23.17 kV} & 
\multicolumn{1}{|l|}{-325.8 V} & \multicolumn{1}{l|}{-0.6 V}      & \multicolumn{1}{l|}{421.9 V} & \multicolumn{1}{|l|}{Run-IIIa}      \\ \hline

                              &                                 &                                 
\end{tabular}
\end{table}

\end{subsubsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}{Wire Plane Assembly}\label{sec:WirePlanes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}*{Wire Winding}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Wires for the LArIAT wire planes are wound to the correct spacing and tension on an independent winding machine before being transferred to the printed circuit boards on which they are installed in the TPC.

\begin{figure}[h!]
\centering
\includegraphics[height=2in]{figures/MamaBear.jpg}
\caption{The wire-winding apparatus in action. Both frames are attached and a single wire has been wound.}
% CAN PROBABLY FIND A BETTER PICTURE!
\label{pic:mamabear}
\end{figure}

Two rectangular steel frames are bolted back-to-back on an apparatus that rotates at a constant speed, shown in Figure \ref{pic:mamabear}. As the frames rotate, wire is drawn from a spool and wrapped around the two frames at constant tension (monitored by a tensiometer in the device paying out the spool). Once the requisite number of wires have been wound, the wires are epoxied onto the steel frames with five-minute epoxy and cut, giving two separate wire planes (one on each frame).
\end{subsubsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}*{Wire Transfer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Once the wire planes have been wound, they must be transferred from the winding frames onto the G10 wire-carrier boards that go into the LArIAT TPC. To achieve this, the frames are unbolted from the winding apparatus and laid over the board onto which the wires are to be transferred, which itself is bolted to a rigid aluminium frame to prevent it from flexing under tension. Careful manual alignment is performed, using guide holes drilled in the board for reference. This alignment is shown in Figure \ref{pic:wiretransfer}.

Once the wires are aligned to the solder pads on the board, they are glued to the board behind the solder pads with a temporary epoxy strip (using five-minute epoxy) to preserve the alignment. This is then followed by a permanent epoxy strip on the inside of the solder pads, using a slow-curing epoxy that is safe for cryogenic conditions. This epoxy is allowed to cure for 12 to 24 hours before the wires are cut behind the temporary strip and the winding frame can be removed.

\begin{figure}[h!]
\centering
\includegraphics[height=2in]{figures/WireTransfer.jpg}
\caption{One of the \textcolor{red}{This can be 4mm or 5 mm wire plane} 3~mm wire planes during transfer, with the wires not yet cut from the winding frame. A steel bar was used for this plane to ensure all wires made good contact with the board.}
\label{pic:wiretransfer}
\end{figure}

\end{subsubsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}*{Soldering of Electrical Connections}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

When the wire transfer is complete, the wires are soldered to their pads using [SOLDER DETAILS HERE], as are the resistor and capacitor components for the U and V planes \textcolor{red}{Which are the values of capacitances and resistances?}. Mylar sheeting is used to protect the active region of the wire planes from evaporating solder flux during this process. Once all wires have been soldered in place, the wires are broken off behind the solder pads and the temporary epoxy strip is removed. The entire board is cleaned with ethyl alcohol to remove any residue of solder flux before the finished wire planes ahead of installation in the TPC.
\end{subsubsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subsubsection}*{Wire Plane Testing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Electrical Testing}\\
\textcolor{red}{Both the test on the RC and on the wire tension are very bad described. According to me it is better to delete the section if a better description can not be provided.}
Every channel on each completed plane is probed with a multimeter and a signal generator to check for electrical continuity, and in the case of the U and V planes, for the correct RC time constant from the components.\\
\textbf{Tension Testing}\\
A laser tensiometer is mounted on a rigid aluminium arm over each completed frame and used to verify the tension on a representative sample of the wires. [QUANTITATIVE RESULTS?]

\end{subsubsection}

\end{subsubsection}

\textcolor{red}{The title says "Cold" but all the electronic, cold and warm, is described}
The LArIAT TPC front-end electronics comprises a 480-channel analog signal path from the TPC wireplanes to the signal digitizers. The front-end system also includes a digital control system for the TPC-mounted electronics, a power supply, and a distribution system.
A block diagram of the overall system is shown in Fig. \ref{pic:FEelectronics}.

\begin{figure}[htbp]
 \centering
 \includegraphics[width=1.0\textwidth]{figures/LArIAT_FE_Electronics.png}
\caption{
Overview of LArIAT Front End electronics. 
} 
\label{pic:FEelectronics}
\end{figure}

The electrical signals on the TPC readout wires are typically quite small, being a direct readout of the ionization of the liquid argon. To achieve a good Signal-to-Noise Ratio (SNR) for such signals, the LArIAT TPC is instrumented with cold amplifiers developed by Brookhaven National Lab (BNL) and mounted directly to the TPC frame inside the liquid argon cryostat. The BNL amplifiers are built as custom Application-Specific Integrated Circuits (ASICs) [ADD reference]. The BNL ASICs adopted in LAriAT are designated as LArASIC, version 4-star.

The LArASICs are mixed signal devices, where the analog amplifier characteristics are controlled by digitally-set parameters. The maximum gain setting of the LArASIC is 25 mV/fc. At this gain a 3.5~fC charge deposition - corresponding to the expected charge arriving at an individual wire from a passing MIP energy deposition - on a readout wire will generate an output with 90~mV amplitude. At the other end of the readout chain, the CAEN V1740 [\textbf{ADD}: CAEN refernece] digitizers have a 12 bit resolution and a maximum input range of 2~VDC, yielding about 0.5~mV LSB. With the analog signal path from LArASIC to the digitizers being designed to provide unity gain, a passing MIP in the TPC is expected to generate a digital signal with amplitude of about 180 ADC counts.  [\textbf{UPDATE}: Dean found gain to be less than unity, add details; what was the measured MIP amplitude?] \textcolor{red}{what is the sampling rate of the board?}

The readout racks containing the signal digitizers are positioned at a distance of $\sim$8~mt from the cryostat and are referenced to a different ground respect to the TPC electronics ground.  The distance minimizes the presence of secondary, tertiary and halo charged particles passing through the digitial electronics.  To prevent problems caused by differing grounds and noise pick-up along the signal transmission line, the single-ended analog signals from the ASICs are transmitted from the cryostat to the readout racks as differential analog pairs, each pair individually shielded.  This is achieved using four types of interconnected cards.  The first type of card in the system is a 48-channel cold motherboard (CMB-48) that mounts directly to the TPC and houses three 16-channel LArASICs per card.  The next card in the signal path is a single cryostat feed through card (FT) that carries the 480 signals, along with power and control lines, across the cryostat boundary.  A set of warm receiver and driver (WRD-48) cards plug directly into the cryostat feed-through and amplify the single-ended TPC signals as differential analog. The differential analog signals are then driven through 8~mt high quality pleated foil cables to a set of differential-to-single-ended (D2S-64) cards, converting the differential signals into single-ended ones, with enough drive capability to allow direct input into an array of CAEN V1740 digitizers.

At the receiving end of the differential path the differential-mode analog signal arrives with common-mode noise cancelled and converted to single-ended analog for the short distance transmission to the CAEN V1740 digitizers.

>>>>

\textcolor{red}{The title says "Cold" but all the electronic, cold and warm, is described}
